Combining Formal and Distributional Models of Predicate Semantics

### 2016-03-18 papers/acl2016/paper.tex

    \path[]
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{nationality}} (2)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (3)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{designed}} (5)
      (2) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (4)
      (5) edge node [sloped, anchor=center, above] {\formalpredicate{located\_in}} (2);
  \end{tikzpicture}
  }
  \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater
  \caption{A subset of the Freebase graph, and some example extracted features
  between \entity{Palladio} and \entity{Italy}.  The actual Freebase relations
  and entity identifiers used are modified here to aid readability.}
  \label{fig:sfe}
\end{figure}

@@

In this section we present our models of predicate semantics.  In
\secref{formal-and-distributional} we describe how we modify Krishnamurthy and
Mitchell's (K\&M's) semantic parser to include features from a formal knowledge
base.  In \secref{computing-pmi} we describe how we select those features for
each predicate.  The remaining two sections then describe other improvements we
made to K\&M's semantic parsing model: lexicalizing preposition and
noun-compound predicates, and using the Freebase graph to select candidate
entities.

\subsection{Formal features for predicate semantics}
\label{sec:formal-and-distributional}

We inject information from a formal knowledge base into our models of predicate
semantics simply by augmenting the learned distributional feature vectors with
formal features.

For each entity and entity pair in the data we compute an SFE feature vector
$\psi(e)$ and $\psi(e_1, e_2)$.  For entity pairs, the vector $\psi(e_1, e_2)$
is a sparse binary vector containing indicator features for all edge sequences
that connect nodes $e_1$ and $e_2$ in the Freebase graph, up to length 4.
These features are shown for the entity pair (\entity{Palladio},
\entity{Italy}) in the example graph in \figref{sfe}.  For entities, we extract
similar features to form the sparse binary vector $\psi(e)$.  These features
are of two types: (1) edge sequences that begin at node $e$ (up to length two),
and (2) edge sequences that begin at node $e$ along with the node at the end of
the sequence.  For example, all of the features listed in \figref{sfe} for the
entity pair (\entity{Palladio}, \entity{Italy}) are also valid features of type
(1) for the entity \entity{Palladio}, as well as the features
\textless\formalpredicate{type}\textgreater and
\textless\formalpredicate{designed}\textgreater.  Examples of of type (2) features
are \textless\formalpredicate{type}\textgreater:\entity{architect}, and
\textless\formalpredicate{nationality}\textgreater:\entity{Italy}.  Intuitively,
features of type (1) capture the fact that an entity participates in particular
kinds of relations, such as designing architectural structures, while features
of type (2) capture the way an entity is related to particular other entities.
Features of type (2) are very specific, and are most useful in practice when
the entity in the feature is a type node, such as with
\textless\formalpredicate{type}\textgreater:\entity{architect}, though occasionally
features of this type involving other entities are also selected in our feature
selection process.

For each category and relation, we select a subset of the SFE features in the
vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
observed features for each entity and entity pair.  The augmented category and
relation probabilities are as follows:

\begin{align*}
  P(c(e)) &= \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
  P(r(e_1, e_2)) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
\end{align*}
where we have added subscripts on the $\psi$ functions to indicate that each
predicate selects its own set of features from the SFE feature vector $\psi$.

We pause here to note that these features obtained from SFE correspond exactly
to a limited set of horn clauses using the Freebase vocabulary, which in turn
can be seen as Freebase queries that define sets of entities or entity pairs.
By associating a number of these features with each predicate and assigning
them weights, what we are effectively doing is mapping language onto a weighted
combination of possible Freebase statements, instead of onto a single Freebase
query, as is typically done in the semantic parsing literature.  This is a
fundamentally new kind of predicate semantics that has not been used previously
in semantic parsers.

Note also that in our combined model there are now three sets of parameters to
be learned by the semantic parser: (1) $\theta$, low-dimensional distributional
vectors trained for each predicate; (2) $\phi$, low-dimensional distributional
vectors trained for each entity and entity pair; and (3) $\omega$, weights
associated with the selected formal SFE features for each predicate.  All of
these parameters are optimized jointly, using the same ranking objective used
by K\&M.

\subsection{Finding relevant features for each predicate}
\label{sec:computing-pmi}

The feature vectors returned by SFE have dimensionality in the tens of
millions.  We do not have near enough data to train that many parameters for
each of our tens of thousands of predicates, nor do we have enough RAM in our
machines to keep that many parameters in memory.  It is thus necessary to
select some small number of informative features for each predicate.  We do
this using pointwise mutual information (PMI).

PMI measures the strength of association between two variables $x$ and $y$; it
is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
associate predicates with SFE features.  However, our SFE features are for each
\emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
SFE features with predicates, we use the training data to find a mapping from
entities and entity pairs to predicates that they have been seen with in the
data.  For example, the phrase ``Italian architect Andrea Palladio'' is
considered a positive training example for the instantiated predicates
$\lexicalpredicate{architect}(\entity{Andrea Palladio})$ and
$\lexicalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  We
then associate the feature vectors for \entity{Andrea Palladio} and
(\entity{Italy}, \entity{Andrea Palladio}) with the predicates
\lexicalpredicate{architect} and \lexicalpredicate{architect\_N/N}, respectively.  For each
predicate $\pi$ and feature $f$, we use these counts to calculate the
probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.  After removing features with
counts below some threshold, we pick the $k$ features with the highest PMI
values for each predicate to use in our model.\footnote{We used $k=100$ in this
paper.}

\subsection{Improved logical forms}
\label{sec:better-lfs}

While we largely follow the semantic parsing framework introduced by K\&M, we
made one important change in how logical forms are generated.  For the running
example we have been using this paper, ``Italian architect Andrea Palladio'',
the relation predicate produced by K\&M's system is
$\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.
\lexicalpredicate{N/N}
does correctly capture the fact that \entity{Italy} is used syntactically as a
noun modifier of \entity{Andrea Palladio}, but it leaves out the additional
information contained in the syntax that ``architect'' was mediating that
noun-noun dependency.  This means that ``U.S. president Barack Obama'' and
``Italian architect Andrea Palladio'' are both modeled using the same relation
predicate, which leads to a very generic and largely useless model for the
predicate \lexicalpredicate{N/N}.  By splitting \lexicalpredicate{N/N} into separate
predicates (\lexicalpredicate{architect\_N/N} and \lexicalpredicate{president\_N/N}), we give
the model the opportunity to learn more fine-grained relation semantics, and we
allow our feature selection pipeline to find much more useful features for
relation predicates.  While it would be ideal to use actual dependency
relations to determine which words to add to the predicate in complex noun
phrases, most current parsers treat these kinds of noun phrases as flat, with
all noun modifiers depending directly on the head of the noun phrase.  We
approximate this ideal by simply taking all words in between the two entities
in a noun phrase as the predicate (e.g., ``Illinois attorney general Lisa
Madigan'' would produce the predicate \lexicalpredicate{attorney\_general\_N/N}).

A similar issue arises with prepositions and possessives.  For a phrase such as
``Barack Obama, president of the U.S.'', K\&M's system would produce the
following relation predicate: $\lexicalpredicate{of}(\entity{Barack Obama},
\entity{U.S.})$.  Because this same predicate (\lexicalpredicate{of}) is used for all
instances of this preposition, the predicate is forced to model too much and
becomes overly generic.  When there is a common noun mediating a prepositional
dependency between two entities, as in the phrase above, we add that noun to
the predicate, giving the instance $\lexicalpredicate{president\_of}(\entity{Barack
Obama}, \entity{U.S.})$.  We do the same for possessives in phrases such as
``Rome, Italy's capital'', producing the predicate \lexicalpredicate{'s\_capital}.

@@

One final way in which we improved K\&M's semantic parser is in how candidate
entities are generated during inference.  Because the distributional-only
predicate models used by K\&M's semantic parser need to learn a vector of
parameters for each entity pair, they cannot give a non-zero score to any
entity pair not seen during training time.  When given a query such as
$\lambda(\entity{x}) \lexicalpredicate{architect\_N/N}(\entity{x}, \entity{Andrea
Palladio})$, K\&M's system only needs to consider the set of entities
$\entity{x}$ that have been seen at training time with \entity{Andrea
Palladio}; all other entities will get a score of 0.

Our predicate models do not have this limitation.  The distributional component
will still give an unseen entity pair a score of 0, as it is identical to K\&M's
model, but the formal component of our models simply computes an observed
feature vector from Freebase for the entity pair.  As long as both entities
appear in Freebase, our model can compute a feature vector and give a non-zero
score.

While this improvement allows us to handle queries over rare entities much
better than a distributional-only model, it also complicates inference, as we
cannot just score entity pairs seen at training time.  Optimizing every query's
score over all of the millions of entities in Freebase is not computationally
feasible.  To make inference tractable, for a given query we restrict
candidates to all entities seen with the query entities during training (as
done by K\&M), as well as all entities directly connected to the query entities
in Freebase, or connected by a mediator node.\footnote{Mediators in Freebase are
used to capture relations with more than two arguments, such as employment
tenure, which has an employer, and employee, a start date, and an end date.}

For some entities, such as the United States, the set of connected entities can
still be intractably large, so we limit this expansion to only those entities
with fewer than 100 directly connected entities.  Our motivation for this is
that this candidate entity generation is most useful for rarely seen entities,
for which we have few or no related entities seen during training.  These
entities also tend to have relatively few connected entities in Freebase.

>>>>

    \path[]
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{nationality}} (2)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (3)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{designed}} (5)
      (2) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (4)
      (5) edge node [sloped, anchor=center, above] {\formalpredicate{located\_in}} (2);
  \end{tikzpicture}
  }
  \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater

  \textbf{Features for \entity{Palladio}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{nationality}\textgreater:\entity{Italy}\\
  \textless\formalpredicate{type}\textgreater:\entity{Architect}\\
  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater \\
  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater:\entity{Italy}

  \caption{A subset of the Freebase graph, and some example extracted features
  between \entity{Palladio} and \entity{Italy}.  The actual Freebase relations
  and entity identifiers used are modified here to aid readability.}
  \label{fig:sfe}
\end{figure}

@@

This section presents our approach to open vocabulary semantic
parsing. Our approach follows the same structure as described in
Section \ref{sec:jayant-semparse}: we generate a surface logical form
from a query, then evaluate it against a probabilistic database with
learned predicate instance probabilities. Section \ref{sec:better-lfs}
describes our logical form generation, which improves the analyses of
noun-mediated relations relative to prior work. Sections
\ref{sec:formal-and-distributional} and \ref{sec:feature-generation}
describe our improved predicate models and the corresponding feature
generation process. Finally, Section \ref{sec:better-candidates}
describes an improvement on candidate entity generation for question
answering.

% In \secref{formal-and-distributional} we describe how we modify
% Krishnamurthy and Mitchell's (K\&M's) semantic parser to include
% features from a formal knowledge base.  In \secref{computing-pmi} we
% describe how we select those features for each predicate.  The
% remaining two sections then describe other improvements we made to
% K\&M's semantic parsing model: lexicalizing preposition and
% noun-compound predicates, and using the Freebase graph to select
% candidate entities.

\subsection{Logical form generation}
\label{sec:better-lfs}

As in K\&M, we generate logical forms from natural language statements
by computing a syntactic CCG parse, then applying a collection of
rules to produce logical forms. However, their logical form analyses
do not model noun-mediated relations well. For example, given the
phrase ``Italian architect Andrea Palladio,'' their system's logical
form would include the relation
$\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea
  Palladio})$. Here, the \lexicalpredicate{N/N} predicate represents a
generic noun modifier relation; however, this relation is too vague
for the predicate model to accurately learn its denotation. A similar
problem occurs with prepositions and possessives, e.g., it is
similarly hard to learn the denotation of the predicate
\lexicalpredicate{of}.

Our system improves the analysis of noun-mediated relations by simply
including the noun in the predicate name. In the architect example
above, our system produces the relation
\lexicalpredicate{architect\_N/N}. It does this by simply
concatenating all intervening noun modifiers between two entity
mentions and including them in the predicate name; for example,
``Illinois attorney general Lisa Madigan'' produces the predicate
\lexicalpredicate{attorney\_general\_N/N}). (While it would be
preferable to use actual dependency relations to determine which words
to add to the predicate, this is not possible because our parser
produces flat analyses of noun phrases where all noun modifiers depend
directly on the head of the noun phrase.) We similarly improve the
analyses of prepositions and possessives to include the head noun. For
example, ``Barack Obama, president of the U.S.'' produces the
predicate instance $\lexicalpredicate{president\_of}(\entity{Barack
  Obama}, \entity{U.S.})$, and ``Rome, Italy's capital'' produces the
predicate \lexicalpredicate{'s\_capital}. This process generates more
specific predicates that we empirically found were easier for the
predicate models to learn.

% While we largely follow the semantic parsing framework introduced by K\&M, we
% made one important change in how logical forms are generated.  For the running
% example we have been using this paper, ``Italian architect Andrea Palladio'',
% the relation predicate produced by K\&M's system is
% $\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.
% \lexicalpredicate{N/N}
% does correctly capture the fact that \entity{Italy} is used syntactically as a
% noun modifier of \entity{Andrea Palladio}, but it leaves out the additional
% information contained in the syntax that ``architect'' was mediating that
% noun-noun dependency.  This means that ``U.S. president Barack Obama'' and
% ``Italian architect Andrea Palladio'' are both modeled using the same relation
% predicate, which leads to a very generic and largely useless model for the
% predicate \lexicalpredicate{N/N}.  By splitting \lexicalpredicate{N/N} into separate
% predicates (\lexicalpredicate{architect\_N/N} and \lexicalpredicate{president\_N/N}), we give
% the model the opportunity to learn more fine-grained relation semantics, and we
% allow our feature selection pipeline to find much more useful features for
% relation predicates.  While it would be ideal to use actual dependency
% relations to determine which words to add to the predicate in complex noun
% phrases, most current parsers treat these kinds of noun phrases as flat, with
% all noun modifiers depending directly on the head of the noun phrase.  We
% approximate this ideal by simply taking all words in between the two entities
% in a noun phrase as the predicate (e.g., ``Illinois attorney general Lisa
% Madigan'' would produce the predicate \lexicalpredicate{attorney\_general\_N/N}).

% A similar issue arises with prepositions and possessives.  For a phrase such as
% ``Barack Obama, president of the U.S.'', K\&M's system would produce the
% following relation predicate: $\lexicalpredicate{of}(\entity{Barack Obama},
% \entity{U.S.})$.  Because this same predicate (\lexicalpredicate{of}) is used for all
% instances of this preposition, the predicate is forced to model too much and
% becomes overly generic.  When there is a common noun mediating a prepositional
% dependency between two entities, as in the phrase above, we add that noun to
% the predicate, giving the instance $\lexicalpredicate{president\_of}(\entity{Barack
% Obama}, \entity{U.S.})$.  We do the same for possessives in phrases such as
% ``Rome, Italy's capital'', producing the predicate \lexicalpredicate{'s\_capital}.

\subsection{Predicate models}
\label{sec:formal-and-distributional}

% TODO: ``query'' features?

We inject information from a knowledge base into our predicate models
by augmenting the learned embeddings with features. The truth
probability of a category instance $c(e)$ or relation instance $r(e_1,
e_2)$ in our model is given by:

\begin{align*}
  P(c(e)) &= \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
  P(r(e_1, e_2)) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
\end{align*}

In the above equation, the $\theta$ and $\phi$ terms are learned
predicate and entity embeddings, as described in Section
\ref{sec:jayant-semparse}. The second term in the sum represents our
new features and their learned weights. $\psi_c(e)$ and $\psi_r(e_1,
e_2)$ are SFE feature vectors for each entity and entity pair; a
different set of features is chosen for each predicate $c$ and $r$ in
order to maximize their usefulness. The terms $\omega_c$ and
$\omega_r$ represent learned weights for these features.

Each SFE feature can be viewed as either a Freebase query or a horn
clause implication rule using the Freebase schema. In both cases, the
feature defines a set of entities (or entity pairs), and the
associated feature weight measures the likelihood that an entity in
this set is also in the denotation of the surface predicate. Our
models include \emph{many} such features for each surface predicate,
effectively mapping each surface predicate onto a \emph{weighted
  combination of Freebase queries}. This approach is fundamentally
different from typical semantic parsers that map language to a single
Freebase query.

In our model, there are now three sets of parameters to be learned:
(1) $\theta$, low-dimensional distributional vectors trained for each
predicate; (2) $\phi$, low-dimensional distributional vectors trained
for each entity and entity pair; and (3) $\omega$, weights associated
with the selected formal SFE features for each predicate.  All of
these parameters are optimized jointly, using the same query ranking
objective used by K\&M.

% For each category and relation, we select a subset of the SFE features in the
% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
% observed features for each entity and entity pair.  The augmented category and
% relation probabilities are as follows:

\subsection{Generating predicate features}
\label{sec:feature-generation}

The feature vectors $\psi_c(e)$ and $\psi_r(e_1, e_2)$ are constructed
using a two-stage process. First, we generate a predicate-independent
feature vector $\psi(e)$ for each entity $e$ and $\psi(e_1, e_2)$ for
each entity pair $(e_1, e_2)$ using SFE. This step generates very
high-dimensional feature vectors, where most of the
features are not relevant for any given predicate. Next, we perform
per-predicate feature selection to identify a subset of these features
that are relevant for each category and relation predicate.

The predicate-independent feature extraction stage computes the
following feature vectors. For entity pairs, the vector $\psi(e_1,
e_2)$ is a sparse binary vector containing indicator features for all
edge sequences that connect nodes $e_1$ and $e_2$ in the Freebase
graph, up to length 4.  For an entity $e$, we extract two kinds of
features: (1) all edge sequences up to length two that begin at $e$,
and (2) the same sequences paired with the entity at their
endpoint. Features of type (1) capture the kinds of relations that an
entity participates in, e.g., designing architectural structures,
while features of type (2) capture relations to other particular
entities. This second kind of feature is most helpful when the
endpoint entity is a type, such as \entity{architect}, although there
are some other valuable features of this kind. \figref{sfe} shows some
example entity and entity pair features extracted from a subset of the
Freebase graph.

% For each category and relation, we select a subset of the SFE features in the
% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
% observed features for each entity and entity pair.  The augmented category and
% relation probabilities are as follows:
% 
% \begin{align*}
%   P(c(e)) &= \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
%   P(r(e_1, e_2)) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
% \end{align*}
% where we have added subscripts on the $\psi$ functions to indicate that each
% predicate selects its own set of features from the SFE feature vector $\psi$.

% The feature vectors returned by SFE have dimensionality in the tens of
% millions.  We do not have near enough data to train that many parameters for
% each of our tens of thousands of predicates, nor do we have enough RAM in our
% machines to keep that many parameters in memory.  It is thus necessary to
% select some small number of informative features for each predicate.  We do
% this using pointwise mutual information (PMI).

The feature selection step uses pointwise mutual information (PMI) to
reduce the number of features considered by the model for each
predicate. The feature vectors generated above have tens of millions
of dimensions, but, for any given surface predicate, only a handful of
these dimensions represent relevant Freebase queries. We select
features by first summing the entity and entity pair feature vectors
seen with each predicate in the training data. For example, the phrase
``Italian architect Andrea Palladio'' is considered a positive
training example for the instantiated predicates
$\formalpredicate{architect}(\entity{Andrea Palladio})$ and
$\formalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea
  Palladio})$. We then add the feature vectors for \entity{Andrea
  Palladio} and (\entity{Italy}, \entity{Andrea Palladio}) to the
feature counts for the predicates \formalpredicate{architect} and
\formalpredicate{architect\_N/N}, respectively. Next, for each predicate
$\pi$ and feature $f$, we use these counts to calculate three
probabilities: $p(\pi, f)$, $p(\pi)$ and $p(f)$. (TODO: how did you
calculate these?). The PMI of a predicate/feature pair is then $\log
\frac{p(\pi, f)}{p(\pi)p(f)}$. After removing features with counts
below a threshold, we pick the $k=100$ features with the highest PMI
values for each predicate to use in our model.

% PMI measures the strength of association between two variables $x$ and $y$; it
% is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
% associate predicates with SFE features.  However, our SFE features are for each
% \emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
% SFE features with predicates, we  For each
% predicate $\pi$ and feature $f$, we use these counts to calculate the
% probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.

@@

A key benefit of our predicate models is that they are able to assign
scores to entity pairs that were never seen in the training data. The
purely-distributional model of K\&M has no basis for assigning these
scores and therefore assumes $P(r(e_1,e_2)) = 0$ for unseen entity
pairs $(e_1,e_2)$. This assumption limits the recall of their system
when it is applied to question answering, as these entity pairs will
not have been observed for many correct, but rare entity answers. In
contrast, our predicate models can score any entity pair: the
distributional component of an unseen pair will be zero, but the SFE
component is always applicable. This benefit allows our model to
considerably improve question answering performance on rare entities.

% One final way in which we improved K\&M's semantic parser is in how candidate
% entities are generated during inference.  Because the distributional-only
% predicate models used by K\&M's semantic parser need to learn a vector of
% parameters for each entity pair, they cannot give a non-zero score to any
% entity pair not seen during training time.  When given a query such as
% $\lambda(x).\lexicalpredicate{architect\_N/N}(x, \entity{Andrea
% Palladio})$, K\&M's system only needs to consider the set of entities
% $\entity{x}$ that have been seen at training time with \entity{Andrea
% Palladio}; all other entities will get a score of 0.
% 
% Our predicate models do not have this limitation.  The distributional component
% will still give an unseen entity pair a score of 0, as it is identical to K\&M's
% model, but the formal component of our models simply computes an observed
% feature vector from Freebase for the entity pair.  As long as both entities
% appear in Freebase, our model can compute a feature vector and give a non-zero
% score.

However, this benefit has an associated drawback: given a logical form
query, it is computationally and statistically undesirable to consider
\emph{all} Freebase entities as answers. Scoring millions of entities
is slow, and furthermore makes it more difficult to identify correct
answers (as their frequency in the candidate set
decreases). Therefore, when answering a query, we compute a set of
candidate entities and only score these candidates. Our candidate set
consists of all entities seen with the query entities in the training
set as well as all entities directly connected to the query entities
in Freebase, or connected by a mediator node.\footnote{Mediators in
  Freebase are used to capture relations with more than two arguments,
  such as employment tenure, which has an employer, and employee, a
  start date, and an end date.}

% While this improvement allows us to handle queries over rare entities much
% better than a distributional-only model, it also complicates inference, as we
% cannot just score entity pairs seen at training time.  Optimizing every query's
% score over all of the millions of entities in Freebase is not computationally
% feasible.  To make inference tractable, for a given query we restrict
% candidates to all entities seen with the query entities during training (as
% done by K\&M), as well as all entities directly connected to the query entities
% in Freebase, or connected by a mediator node.\footnote{Mediators in Freebase are
% used to capture relations with more than two arguments, such as employment
% tenure, which has an employer, and employee, a start date, and an end date.}

Unfortunately, for some entities, such as the United States, the set
of connected entities can be intractably large; we therefore limit
this expansion to only those entities with fewer than 100 directly
connected entities.  Our motivation for this is that this candidate
entity generation is most useful for rarely seen entities, for which
we have few or no related entities seen during training.  These
entities also tend to have relatively few connected entities in
Freebase.
